---
title: "Quarto Document"
author: "Arwenn K"
format: html
editor: visual
---

## Pitfall trap and ground quadrat analyses

Welcome! Today we're diving into some pitfall trap data from 2024, collected (with permits - don't worry) in the Potberg region of De Hoop, Western Cape, South Africa. I set out to investigate if there was a change in local ant communities with a change in vegetation cover from invasive eucalyptus trees, to natural fynbos.

Many hours were spent sorting, counting and identifying the ants in the 32 pitfall traps, leaving a sum total of 886 ants. As you can imagine, I've had enough of them...

Let's get started.

### Loading packages:

for these analyses we'll use the beloved *tidyverse* package and *readxl*.

```{r}
#| label: loading packages
## Install packages
install.packages("tidyverse")
install.packages("readxl")

## Load Packages
library(tidyverse)
library(readxl)
```

You can add options to executable code like this

```{r}
#| echo: false
2 * 2
```

The `echo: false` option disables the printing of code (only output is displayed).
